\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-07-25 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added replace_use_mpi_with_include_mpif_dot_h.pl

@@

>>>>

If your compiler has problems with the \texttt{use mpi} statements that are used in the code, use the script called 
\texttt{replace\_use\_mpi\_with\_include\_mpif\_dot\_h.pl} in the root directory to replace all of them with \texttt{include 'mpif.h'} automatically.

@@

NOTE FROM JULY 2013: OpenMP support is maybe / probably not maintained any more.
Thus the section below is maybe obsolete.
